Model LF

### 2022-09-19 max_dp endogen stød.Rmd
commit lit review

wage_ds_01 = Shock_1$simulation$wage_ds
```

@@

plot(pc_ds_01, col= "red"); lines(pc_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds

@@

>>>>

wage_ds_01 = Shock_1$simulation$wage_ds

yd_g_01 = Shock_1$simulation$yd_g

nben_h_01 = Shock_1$simulation$nben_h
```

@@

plot(pc_ds_01, col= "red"); lines(pc_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(nben_h_01, col= "red"); lines(nben_h_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
ik_03 = Shock_3$simulation$ik

@@

plot(ik_03, col= "red"); lines(ik_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
